---
title: 'IB98D0 Analysis Code by Group 36'
output: html_document
date: "2025-02-03"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(knitr)
library(tidyr)
```

## Step 1. Data Preparation
```{r loar_data}
# Load Data
df <- read.csv("ADAproject_2025_data.csv",
               header = T,
               stringsAsFactors = FALSE)

# Set categorical variable
df$Variant <- factor(df$Variant)
```

### Data Cleaning 
```{r data_cleaning}

# When complt_init, complt_fin and fully_complt are not equal, it indicates that some loans were not reviewed by both the loan officer and the AI.
# These loans do not meet our experimental criteria and should be filtered out.
df_1 <- df %>%
  filter(complt_init == complt_fin, complt_fin == fully_complt, fully_complt == badloans_num + goodloans_num)

# Aggregate the data to the user-level
df_2 <- df_1 %>%
  group_by(Variant, loanofficer_id) %>%
  summarise(
    typeI_init = sum(typeI_init, na.rm = TRUE),
    typeI_fin = sum(typeI_fin, na.rm = TRUE),
    typeII_init = sum(typeII_init, na.rm = TRUE),
    typeII_fin = sum(typeII_fin, na.rm = TRUE),
    badloans_num = sum(badloans_num, na.rm = TRUE),
    mean_confidence_init = mean(confidence_init_total, na.rm = TRUE),
    mean_confidence_fin = mean(confidence_fin_total, na.rm = TRUE),
    .groups = "drop")
# Compute the recall and precision before and after using the model. Then calculate the difference between recall, precision and confidence score.
df_2 <- df_2 %>%
  mutate(recall_init = (badloans_num - typeII_init) / badloans_num, 
         precision_init = (badloans_num - typeII_init) / (badloans_num - typeII_init + typeI_init), 
         recall_fin = (badloans_num - typeII_fin) / badloans_num, 
         precision_fin = (badloans_num - typeII_fin) / (badloans_num - typeII_fin + typeI_fin),
         recall_improvement = recall_fin - recall_init,
         precision_improvement = precision_fin - precision_init,
         confidence_improvement = (mean_confidence_fin - mean_confidence_init) / 1000 )
```

## Step 2. Data Analysis: Hypothesis Testing

OEC (Overall Evaluation Criteria) = w1 * recall_per_officer + w2 * precision_per_officer + w3 * confidence_improvement

w1, w2, and w3 are weights. Considering the objectives of the loan company, we prioritize reducing the erroneous acceptance of bad loans (FN) over reducing the missed approvals of good loans (FP). This is because a bad loan can result in the long-term loss of the entire principal, whereas missing a good loan only reduces the potential profit from interest. Therefore, a higher weight (0.5) is assigned to recall. As for the confidence score, it is less critical to the company’s revenue objectives, so we assign it a lower weight (0.1).

*Hypothesis*: Implementing the new model will improve the quality of loan decision-making. (single-tailed t-test)

*Another way*: There's a difference in loan decision-making quality between the Control (existing model) and the Treatment (new model) variants. (two-tailed t-test)

```{r data_select} 
# Select the columns to test dataset
test_data <- df_2 %>%
  select(Variant, loanofficer_id, recall_improvement, precision_improvement, confidence_improvement)
```


```{r test}

# OEC = w1*recall_per_officer + w2*precision_per_officer + w3*confidence_improvement
w1 <- 0.5
w2 <- 0.4
w3 <- 0.1
test_data <- test_data %>%
  mutate(OEC = w1 * recall_improvement + w2 * precision_improvement + w3 * confidence_improvement)

t_result1 <- t.test(OEC ~ Variant, 
       data = test_data, 
       var.equal = FALSE)
t_result2 <- t.test(recall_improvement ~ Variant, 
       data = test_data, 
       var.equal = FALSE)
t_result3 <- t.test(precision_improvement ~ Variant, 
       data = test_data, 
       var.equal = FALSE)
t_result4 <- t.test(confidence_improvement ~ Variant,
       data = test_data, 
       var.equal = FALSE)

print(t_result1)
print(t_result2)
print(t_result3)
print(t_result4)
```
The treatment (new computer model) significantly *increased* (p = 0.0003917 < 0.001) OEC compared to Control (existing model).
The treatment  significantly *increased* (p = 0.01097 < 0.05) recall_improvement compared to Control.
The treatment  significantly *increased* (p = 0.0001407 < 0.001) precision_improvement compared to Control.
The treatment  showed *no statistically significant difference* (p = 0.3626) in confidence improvement compared to the control .

```{r adjust}

#
p.values <- c(t_result1$p.value, t_result2$p.value, t_result3$p.value, t_result4$p.value)

p.adjusted.bh <- p.adjust(p.values, method = "BH")

print(p.adjusted.bh)


```

After adjusting p-values for multiple comparisons using the Bonferroni-Holm method, the results remained consistent.

##Step 3. Data Analysis: Compute Difference in Mean OEC (Actual Value & %) between Variants

```{r compare}
#
# Compute mean OEC for each Variant
mean_values_each_Variant <- test_data %>%
  group_by(Variant) %>%
  summarise(
    mean_OEC = mean(OEC),
    mean_recall = mean(recall_improvement),
    mean_precision = mean(precision_improvement),
    mean_confidence = mean(confidence_improvement)
  )

# View mean OEC and the relative values.
print(mean_values_each_Variant)

# Compute pairwise % differences in OEC and relative values between the Control and Treatment
pairwise_diff <- mean_values_each_Variant %>%
  summarise(
    Diff_OEC_Treatment_Control = mean_OEC[Variant == "Treatment"] - mean_OEC[Variant == "Control"],
    Perc_OEC_Treatment_Control = (Diff_OEC_Treatment_Control / mean_OEC[Variant == "Control"]) * 100,
    Diff_Recall_Treatment_Control = mean_recall[Variant == "Treatment"] - mean_recall[Variant == "Control"],
    Perc_Recall_Treatment_Control = (Diff_Recall_Treatment_Control / mean_recall[Variant == "Control"]) * 100,
    Diff_Precision_Treatment_Control = mean_precision[Variant == "Treatment"] - mean_precision[Variant == "Control"],
    Perc_Precision_Treatment_Control = (Diff_Precision_Treatment_Control / abs(mean_precision[Variant == "Control"])) * 100,
    Diff_Confidence_Treatment_Control = mean_confidence[Variant == "Treatment"] - mean_confidence[Variant == "Control"],
    Perc_Confidence_Treatment_Control = (Diff_Confidence_Treatment_Control / mean_confidence[Variant == "Control"]) * 100
  )

# View pairwise differences
print(pairwise_diff)
pairwise_diff_t <- pairwise_diff %>%
  pivot_longer(cols = everything(), names_to = "Differenece", values_to = "Value") %>%
  kable(digits = 4)

print(pairwise_diff_t)

```

Treatment (new model) significantly *increased* (p < 0.001) OEC compared to Control by 932.8%.
Treatment significantly *increased* (p < 0.05) recall compared to Control by 690.4%.
Treatment significantly *increased* (p < 0.001) precision compared to Control by 1010.8%.
However, the difference in confidence compared to Control was *not statistically significant* (p = 0.3626), with only a 51.9% increase.

The improvements in OEC, recall, and precision suggest a *practically significant* boost, while the confidence results indicate no meaningful change compared to the existing model.


## Step 4. Data Analysis: Compute & Interpret Effect Size (Cohen's d)
```{r effectsize}
library(effectsize)

# Effect size of OEC
cohen_d_OEC <- cohens_d(test_data$OEC[test_data$Variant == "Treatment"], 
                        test_data$OEC[test_data$Variant == "Control"])

# Effect size of recall_improvement
cohen_d_Recall <- cohens_d(test_data$recall_improvement[test_data$Variant == "Treatment"], 
                           test_data$recall_improvement[test_data$Variant == "Control"])

# Effect size of precision_improvement
cohen_d_Precision <- cohens_d(test_data$precision_improvement[test_data$Variant == "Treatment"], 
                              test_data$precision_improvement[test_data$Variant == "Control"])

# Effect size of confidence_improvement
cohen_d_Confidence <- cohens_d(test_data$confidence_improvement[test_data$Variant == "Treatment"], 
                               test_data$confidence_improvement[test_data$Variant == "Control"])

print(cohen_d_OEC)
print(cohen_d_Recall)
print(cohen_d_Precision)
print(cohen_d_Confidence)

```

Treatment (new model) significantly *increased* (p < 0.001, d = 1.06) OEC compared to Control by 932.8%.
Treatment significantly *increased* (p < 0.001, d = 0.67) recall compared to Control by 690.4%.
Treatment significantly *increased* (p < 0.001, d = 1.04) precision compared to Control by 1010.8%.
The difference in confidence compared to Control was *not statistically significant* (p = 0.3626, d = 0.26), with only a 51.9% increase.

The improvements in OEC, recall, and precision demonstrate both *statistical and practical significance*, considering the p-value, Cohen's d effect size, and the percentage change. However, the observed difference in confidence does not exhibit statistical significance.




## Recommendations About the Data :Compute Required Sample Size for Desired Power Level & Effect Size

To ensure the feasibility of the experiment, when we assume an effect size of 1.06(from our OEC effect size) for the sample difference, the required sample size is approximately 15 samples per group.

```{r datasize}
library(pwr)
pwr.t.test(d = 1.06, power = 0.8, sig.level = 0.05, type = "two.sample")
